---
title: "Data Analysis - Real Estate"
description: |
  Created earlier this year, the following post displays residential real estate sales in Sacramento, California (My hometown!)
  
author:
  - name: Grace Christensen
    url: https://example.com/norajones
date: March 2, 2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

Using a sample of Sacramento, California real estate transactions, I created a map highlighting the location and price of residential real estate transactions.

The results are shown below with additional details following.

```{r}

library(tidyverse)
library(lubridate)
library(readxl)
library(janitor)
library(glue)
library(leaflet)
library(RColorBrewer)
library(htmlwidgets)
library(htmltools)
library(tigris)
library(tmap)
library(tmaptools)

sac_sales <- read.csv("https://support.spatialkey.com/wp-content/uploads/2021/02/Sacramentorealestatetransactions.csv")

residentialsales <- subset(sac_sales, type == "Residential")

leaflet(data = residentialsales) %>%
  addTiles() %>%
  setView(-121.49935907688821, 38.62485634611972, zoom = 10) %>%
  addCircles(lng = ~longitude, lat = ~latitude,
             weight = 1, radius = ~sqrt(price), popup = ~city)

```

It is important to note that this data does not include any condo or multi-family dwellings.

Additionally, each dot on this map represents one sale with the size of the data point reflecting the price the home sold for.  The bigger the dot, the bigger the sale.
